---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
options(max.print=10)
options(warn=-1)
require(dplyr)
require(ggplot2)
require(GGally)
require(RSQLite)
require(reshape2)
require(DescTools)
require(Rmisc)

#AI DATA
#db_path = "../resources/ai_2019-03-10_20-18-31_100iter.db"
#MODEL DATA 
db_path = "../resources/model_2019-03-10_22-11-21_100iter.db"
con <- RSQLite::dbConnect(RSQLite::SQLite(), db_path)
victory_stats <- dbReadTable(con, "result_analysis")
game_data <- dbReadTable(con, "game")
dbDisconnect(con)

victory_stats <- victory_stats %>% select(Size, C, Ds, Dc, victory)

```

```{r}
colnames(victory_stats)<- c("sizeMap", "sizeCoalition", "intSolo", "intCoalition", "victory")
victory_stats <- victory_stats %>% mutate(intDiff=intSolo-intCoalition)
victory_stats <- victory_stats %>% group_by(sizeMap,sizeCoalition,intSolo,intCoalition,intDiff) %>% summarize(victory_percent=sum(victory=="True")/n())  %>% ungroup() 
victory_stats$sizeCoalition <- as.character(victory_stats$sizeCoalition)
victory_stats$intSolo <- as.character(victory_stats$intSolo)
victory_stats$intCoalition <- as.character(victory_stats$intCoalition)
victory_stats$intDiff <- as.character(victory_stats$intDiff)
victory_stats <- victory_stats[order(-victory_stats$victory_percent),]
```

```{r}
meanfunc <- function(df) {MeanCI(df, conf.level=0.95)}
all_melted_data <- melt(victory_stats, id.vars="victory_percent")

df <- all_melted_data %>% group_by(variable, value) %>% summarize(min_val= min(victory_percent), max_val=max(victory_percent), average_victory_percentage=meanfunc(victory_percent)[1], err_lwr=meanfunc(victory_percent)[2], err_upr=meanfunc(victory_percent)[3])
```
# Victory conditions overview
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
analysis_graph<- function(df, title){
  
  return(ggplot(df, aes(x=value, ymin=min_val, y=average_victory_percentage, ymax=max_val, color=average_victory_percentage))+
    geom_linerange(data=subset(df,variable=="sizeMap"))+
    geom_crossbar(data=subset(df,variable=="sizeMap"), aes(ymin=err_lwr, ymax=err_upr))+
    geom_linerange(data=subset(df,variable=="sizeCoalition")) +
    geom_crossbar(data=subset(df,variable=="sizeCoalition"), aes(ymin=err_lwr, ymax=err_upr))+
    geom_linerange(data=subset(df,variable=="intSolo"))+
    geom_crossbar(data=subset(df,variable=="intSolo"), aes(ymin=err_lwr, ymax=err_upr))+
    geom_linerange(data=subset(df,variable=="intCoalition"))+
    geom_crossbar(data=subset(df,variable=="intCoalition"), aes(ymin=err_lwr, ymax=err_upr))+
    geom_linerange(data=subset(df,variable=="intDiff"))+
    geom_crossbar(data=subset(df,variable=="intDiff"), aes(ymin=err_lwr, ymax=err_upr))+
    scale_color_gradient2(name="Taux de victoire de la coalition", midpoint=0.5, mid="gray70", high="dodgerblue", low="firebrick2")+
    ggtitle(title)+
      ylab("")+
      xlab("")
    )
}

analyze_data <- function(victory_stats, title){
  all_melted_data <- melt(victory_stats, id.vars="victory_percent")
  df <- all_melted_data %>% group_by(variable, value) %>% summarize(min_val= min(victory_percent), max_val=max(victory_percent), average_victory_percentage=meanfunc(victory_percent)[1], err_lwr=meanfunc(victory_percent)[2], err_upr=meanfunc(victory_percent)[3])
  return(analysis_graph(df, title)+
    facet_grid(.~variable,scales = "free_x"))
}


analyze_binned_data<- function(binned_data, title){
  all_melted_data <- melt(binned_data, id.vars=c("victory_percent", "bin"))
  df <- all_melted_data %>% group_by(variable, value, bin) %>% summarize(min_val= min(victory_percent), max_val=max(victory_percent), average_victory_percentage=meanfunc(victory_percent)[1], err_lwr=meanfunc(victory_percent)[2], err_upr=meanfunc(victory_percent)[3])
  return(analysis_graph(df, title)+
    facet_grid(bin~variable,scales = "free_x"))
}

```

# Analyzing victory stats:

## whole data set

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
analyze_data(victory_stats, "Représentation du taux de victoire selon l'ensemble des paramètres")
```

## Locking victory percents into 5 equally spaced intervals

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
binned_data <- victory_stats %>% group_by(bin=cut(victory_percent, seq(min(victory_percent), max(victory_percent), by = (max(victory_percent)-min(victory_percent))/4), include.lowest=T))

analyze_binned_data(binned_data, "Représentation du taux de victoire selon le taux de victoire")
```




## Locking sizeCoalition into 5 equally spaced intervals

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
binned_data <- victory_stats %>% group_by( bin=sizeCoalition )
analyze_binned_data(binned_data, "Représentation du taux de victoire selon la taille de la coalition")
```


## Locking intSolo into 5 equally spaced intervals

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
binned_data <- victory_stats %>% group_by(bin=intSolo)
analyze_binned_data(binned_data, "Représentation du taux de victoire selon l'intelligence du joueur solo")
```


## Locking intCoalition into 5 equally spaced intervals

```{r echo=FALSE, message=FALSE, warning=FALSE}
binned_data <- victory_stats %>% group_by(bin=intCoalition)
analyze_binned_data(binned_data, "Représentation du taux de victoire selon l'intelligence de la coalition")
```

## Locking area into 5 equally spaced intervals

```{r echo=FALSE, message=FALSE, warning=FALSE}
binned_data <- victory_stats %>% group_by(bin=sizeMap)
analyze_binned_data(binned_data, "Représentation du taux de victoire selon la taille de carte")
```

## Locking intSolo-intCoalition into 5 equally spaced intervals

```{r echo=FALSE, message=FALSE, warning=FALSE}
binned_data <- victory_stats %>% group_by(bin=intDiff)
analyze_binned_data(binned_data, "Représentation du taux de victoire selon l'écart d'intelligence")
```